The Hot Hand Fallacy in Call of Duty Search and Destroy

### 2022-08-29 paper/paper.Rmd
atl fixes

We adopt the terminology "series" to refer to a single best-of-11 matchup, so as to mirror the terminology of playoff series in professional leagues like the National Basketball Association (NBA), National Hockey League (NHL), and Major League Baseball (MLB). A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD for the purposes of this paper.

We note that SnD is not the only game mode played in competitive CoD.[^4] Teams play in a head-to-head, best-of-five format, where SnD is always played as the second and fifth game modes. The best-of-five matchup could also be called a "series", but since we analyze only the SnD games, we refer to the SnD games as series.

@@

    Outside of tournaments, teams all play each other twice throughout the season, constituting qualifiers. Each team gets to play the higher-seeded role once in their head-to-head matchups with a given team, despite their win-loss records.

@@

```{=tex}
\begin{equation}\label{eq:chi-squ}
\chi^2 = \sum_{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}
\end{equation}
```
in which $\hat{\Phi}(r)$ and $\Phi(r)$ represent the expected and observed round win proportions respectively, and $R = [6, 7, 8, 9, 10, 11]$ for CoD SnD. The null hypothesis is that the test statistic is chi-squared distributed, where the number of degrees of freedom is $\vert R \vert -1 = 5$ for Cod SnD.

@@

As implied by MS's Theorem 1, we should expect the proportion of round wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|k,r}_{MS}$, to be strictly less than $p^{+|r}$. Although one might be tempted to mirror the equal proportions hypothesis testing performed by MS, our context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings, unaffected by opposition.[^14] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series. The Bernoulli trial success probability, i.e. single round win percentage in CoD SnD, is not independent of the opponent. Consequently, a statistical test of the difference in $\hat{P}^{+|k,r}$ and $\hat{P}^{-|kr}$, as performed by MS to evaluate their hypothesis regarding post-streak success rate, is not completely appropriate, although useful as a reference.

[^14]: GVT also perform statistical tests on shots from players in live games, i.e. "observational" data, but they note that their findings are likely affected by player shot selection in the face of defensive strategy by the opposing team.

@@

One can consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series given the length of the series ($r$ rounds), the "notional" proportion $\hat{P}^{+|k,r}_0$. The Bernoulli round win probability underlying $\hat{P}^{+|k,r}_0$ is

```{=tex}
\begin{equation}\label{eq:pwkr}
p_0(\text{win} | k, r) = p^{+|k,r}_0 := \begin{cases}
  \frac{m - k}{r - k} & \text{team wins series}, \\
  \frac{s - m - k}{r - k} & \text{team loses series},
\end{cases}
\end{equation}
```
for $r \in R$ and $m$ from Equation \ref{eq:m}.

We can perform a two-tailed binomial test to evaluate the null hypothesis $\omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$ (where $0 \leq \omega_0 \leq 1$). If there are $r^+$ observed successes in a sample of $r$ trials and we expect that there should be $r * \omega_0$, the probability of arriving at this expected number of successes is

```{=tex}
\begin{equation}\label{eq:binom}
\binom {r}{r^+} \omega^{r^+}(1-\omega)^{r-r^+}.
\end{equation}
```
Treating the notional proportion $\hat{P}^{+|k,r}_0$ as the null $\omega_0$ and plugging in the observed proportion $P^{+|k,r}$ for $\omega$ in Equation \ref{eq:binom} (treating proportions as probabilities), we can evaluate the null hypothesis that the observed proportion of post-streak round wins is equal to the notional proportion, given streak length $k$ and series length $r$. If we can reject this null hypothesis, then we can consider team momentum, represented by post-streak success, plausible.

@@

We can further decompose Equation \ref{eq:pwkr} by the round $i$ (where $i \leq r$) in which the streak of length $k$ carries into.

```{=tex}
\begin{equation}\label{eq:pwkri}
p_0(\text{win} | k, r, i) = p^{+|k,r,i}_0 = \begin{cases}
  \frac{m - k}{r - k}, & \text{team wins series}, i \neq r, \\
  1, & \text{team wins series}, i = r, \\
  \frac{s - m - k}{r - k}, & \text{team loses series}, i \neq r, \\
  0, & \text{team loses series}, i = r.
\end{cases}
\end{equation}
```
Again, we can apply a binomial test to evaluate the hypothesis that the expected proportions, $\hat{P}^{+|k,r,i}_0$ and $\hat{P}^{+|k,r,i}_{MS}$ separately, are equal to the observed proportion $P^{+|k,r}$.

@@

Stepping back from the (one-sided) perspective of a single team's round win probability when streaking, one can attempt to detect the hot hand phenomenon more broadly with a Wald-Wolfowitz runs test. Under the null hypothesis, the number of runs in a sequence of $r$ trials is a random variable that can take on values $+$ or $-$ and arrive at $r^+$ successes ($r^- = r - r^+$ failures), with the following mean $\mu$ and variance $\sigma^2$:

```{=tex}
\begin{equation}\label{eq:ww}
\mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}.
\end{equation}
```
To incorporate our findings regarding constant round win probability, We can specify that $\Pr(r^+) = \phi$ (and, conversely, that $\Pr(r^-) = 1 - \phi$).

One can subset the observed series sequences, $\zeta(r)$, to those that violate the null hypothesis for the runs test and perform a test of equal proportions, where the null is that the observed proportion of a sequence relative to all possible sequences, $P(\zeta) = P^\zeta$, is equal to the expected proportion of the sequence relative to all possible sequences, $\hat{P}^\zeta$. The test statistic is

@@

and where $N^\zeta$ and $\hat{N}^\zeta$ are the observed and expected number of sequences respectively. The null hypothesis is that $z$ is normally distributed. If $z > +z_{(1-\alpha)/2}$ or $z < -z_{(1-\alpha)/2}$ at a significance level $\alpha$, we can reject the null hypothesis for such sequences and build an argument in support of the hot hand effect.

@@

Using Equation \ref{eq:chi-squ}, we find that $\chi^2 = 16.0$ ($p$-value of 0.0068) for $\phi_0 = 0.5$. Thus, we can comfortably reject the constant probability hypothesis for the null $\phi_0 = 0.5$, even at a confidence level of $\alpha = 0.01$.

@@

Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected series lasting $r$ rounds, the expected proportion of series given $\phi_0 = 0.5$, $\hat{\Phi}_0(r)$, and the observed proportions, $\Phi(r)$.

@@

\end{table}
```
Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability that we find when applying the three methods suggested by Mosteller [-@mosteller1952]. Each is approximately equal to 0.575. When applying Equation \ref{eq:chi-squ}, each results in a $\chi^2$ value for which we cannot reject the constant probability null hypothesis. Note that rejection of the null hypothesis is the baseline and failure to reject the null is the non-trivial result, contrary to most statistical analysis.

@@

\end{table}
```
Table \ref{tbl:alternative-constant-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^15] We observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$. $\hat{\Phi}_2(r)$ is also closer to the observed $\Phi(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.

@@

\end{table}
```
Observing that the null hypothesis acceptance shown in Table \ref{tbl:mosteller-methods-results}, along with the observation that $\hat{\Phi}_2(r)$ reasonably matches $\Phi(r)$ (in comparison to $\hat{\Phi}_0(r)$), we can say that the constant round win probability assumption is valid in CoD SnD series with the appropriate choice of $\phi$ ($\approx 0.575$).

@@

Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins.[^16] Table \ref{tbl:pwkr} compares the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively, with the observed round win proportion, $P^{+|kr}$, following streaks of $k=3$ round wins given the series outcome.

[^16]: Three happens to also be a reasonable number for series that last at maximum 11 rounds.

@@

\end{table}
```
With the exception of $\hat{P}^{+|k,r}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins, all un-adjusted binomial test $p$-values are greater than the $\alpha = 0.05$ confidence level, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win proportions are different than the observed proportion. However, after adjusting the $p$-values with the Benjamini and Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.[^17]

[^17]: As noted before, the MS expectations may be unreliable for CoD SnD, so one is inclined to prefer the results of the notional binomial tests.

When performing the same tests for streaks of two, four, and five, there is no case in which we can reject the binomial null hypothesis for the expected notional proportion $\hat{P}^{+|k,r}_0$ (even before the BY p-value correction). The null hypothesis can only be rejected for the expected MS proportion $\hat{P}^{+|k,r}_{MS}$ when $k = 5, r = 7$ after applying the BY p-value correction.[^18]

>>>>

We adopt the terminology "series" to refer to a single best-of-11 matchup, so as to mirror the terminology of playoff series in professional leagues like the National Basketball Association (NBA), National Hockey League (NHL), and Major League Baseball (MLB). A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD for the purposes of this paper. Note that SnD is not the only game mode played in competitive CoD.[^4] Teams play in a head-to-head, best-of-five format, where SnD is always played as the second and fifth game modes. The best-of-five matchup could also be called a "series", but since we analyze only the SnD games, we refer to the SnD games as series.

@@

    Outside of tournaments, teams play each other twice throughout the season, constituting qualifiers. Each team gets to play the higher-seeded role once in their head-to-head matchups with a given team.

    This format has minimized the range of rates at which teams start series playing offense. The highest rate at which a team has started their series playing defense across all tournament and qualifier SnD series in a single season is 66% (31 of 47). The lowest is 38% (16 of 42).

@@

```{=tex}
\begin{equation}\label{eq:chi-squ}
\chi^2 = \sum_{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}
\end{equation}
```
in which $\hat{\Phi}(r)$ and $\Phi(r)$ represent the expected and observed round win proportions respectively, and $R = [6, 7, 8, 9, 10, 11]$ for CoD SnD. The null hypothesis is that the test statistic is chi-squared distributed, where the number of degrees of freedom is $\vert R \vert -1 = 5$ for Cod SnD. TODO: Make a note about $\alpha$

@@

As implied by MS's Theorem 1, we should expect the proportion of round wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|k,r}_{MS}$, to be strictly less than $p^{+|r}$. However, we should not mirror the equal proportions hypothesis testing performed by MS.

Our context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings, unaffected by opposition.[^14] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series. The Bernoulli trial success probability, i.e. single round win percentage in CoD SnD, is not independent of the opponent. Consequently, a statistical test of the difference in $\hat{P}^{+|k,r}$ and $\hat{P}^{-|kr}$, as performed by MS to evaluate their hypothesis regarding post-streak success rate, is not completely appropriate, although useful as a reference.

[^14]: GVT also perform statistical tests on shots from players in live games, i.e. "observational" data, but they note that their findings are likely affected by player shot selection in the face of tactics by the opposing team.

@@

One can consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series given the final length of the series ($r$ rounds), the "notional" proportion $\hat{P}^{+|k,r}_0$. The Bernoulli round win probability underlying $\hat{P}^{+|k,r}_0$ is

```{=tex}
\begin{equation}\label{eq:pwkr}
p_0(\text{win} | k, r) = p^{+|k,r}_0 := \begin{cases}
  \frac{m - k}{r - k} & \text{team wins series}, r > m; \\
  1 & \text{team wins series}, r = m; \\
  \frac{s - m - k}{r - k} & \text{team loses series}, r > m + k; \\
  0 & \text{team loses series}, r = m + k,
\end{cases}
\end{equation}
```

where $r \in R$ for $m$ from Equation \ref{eq:m}.

We can perform a two-tailed binomial test to evaluate the null hypothesis $\omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$ (where $0 \leq \omega_0 \leq 1$). If there are $r^+$ observed successes in a sample of $r$ trials, the probability of arriving at this expected number of successes is

```{=tex}
\begin{equation}\label{eq:binom}
\binom {r}{r^+} \omega^{r^+}(1-\omega)^{r-r^+}.
\end{equation}
```

We should expect that there should be $r * \omega_0$ successes.

TODO: Simplify this first sentence.

Treating the notional proportion $\hat{P}^{+|k,r}_0$ as the null $\omega_0$ and plugging in the observed proportion $P^{+|k,r}$ for $\omega$ in Equation \ref{eq:binom} (treating proportions as probabilities), we can evaluate the null hypothesis that the observed proportion of post-streak round wins is equal to the notional proportion, given streak length $k$ and series length $r$. If we can reject this null hypothesis, then we can consider team momentum, represented by post-streak success, plausible.

@@

We can further decompose Equation \ref{eq:pwkr} by the round $i$ (where $k < i \leq r$) in which the streak of length $k$ carries into.

```{=tex}
\begin{equation}\label{eq:pwkri}
p_0(\text{win} | k, r, i) = p^{+|k,r,i}_0 = \begin{cases}
  \frac{m - k}{r - k} & \text{team wins series}, i \neq r; \\
  1 & \text{team wins series}, i = r; \\
  \frac{s - m - k}{r - k} & \text{team loses series}, i \neq r, r > m + k; \\
  0 & \text{team loses series}, i = r \text{ or } r = m + k.
\end{cases}
\end{equation}
```
Again, we can apply a binomial test to evaluate the hypothesis that the expected proportion--$\hat{P}^{+|k,r,i}_0$ and $\hat{P}^{+|k,r,i}_{MS}$ separately--is equal to the observed proportion $P^{+|k,r,i}$.

@@

Stepping back from the perspective of a single team's round win probability when streaking, one can attempt to detect the hot hand phenomenon more broadly with a Wald-Wolfowitz runs test. Under the null hypothesis, the number of runs in a sequence of $r$ trials is a random variable that can take on values $+$ or $-$ and arrive at $r^+$ successes ($r^- = r - r^+$ failures), with the following mean $\mu$ and variance $\sigma^2$:

```{=tex}
\begin{equation}\label{eq:ww}
\mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}.
\end{equation}
```
To incorporate our findings regarding constant round win probability, we can specify that $\Pr(r^+) = \phi$.

One can subset the observed series sequences, $\zeta(r)$, to those that violate the null hypothesis for the runs test and perform a test of equal proportions, where the null is that the observed proportion of a sequence relative to all possible sequences, $P^\zeta$, is equal to the expected proportion of the sequence relative to all possible sequences, $\hat{P}^\zeta$. The test statistic is

@@

and where $N^\zeta$ and $\hat{N}^\zeta$ are the observed and expected number of sequences respectively. The null hypothesis is that $z$ is normally distributed. If we can reject the null hypothesis for such sequences and build an argument in support of the hot hand effect.

@@

Using Equation \ref{eq:chi-squ}, we find that $\chi^2 = 16.0$ ($p$-value of <0.01) for $\phi_0 = 0.5$. Thus, we can comfortably reject the constant probability hypothesis for the null $\phi_0 = 0.5$ at a confidence level of $\alpha = 0.05$.

@@

Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected proportion of series lasting $r$ rounds given $\phi_0 = 0.5$, $\hat{\Phi}_0(r)$, as well as the observed proportions, $\Phi(r)$.

@@

\end{table}
```
Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability assumptions, each approximately equal to 0.575. When applying Equation \ref{eq:chi-squ}, each results in a $\chi^2$ value for which we cannot reject the constant probability null hypothesis.

@@

\end{table}
```
Table \ref{tbl:alternative-constant-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^15] We observe that $\hat{\Phi}_2(r)$ more closely matches $\Phi(r)$ than $\hat{\Phi}_0(r)$.

@@

\end{table}
```
Observing the null hypothesis acceptance shown in Table \ref{tbl:mosteller-methods-results}, along with the observation that $\hat{\Phi}_2(r)$ reasonably matches $\Phi(r)$, we can say that the constant round win probability assumption is valid in CoD SnD series with the appropriate choice of $\phi$ ($\approx 0.575$).

@@

Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins. Table \ref{tbl:pwkr} compares the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively, with the observed round win proportion, $P^{+|k,r}$, following streaks of $k=3$ round wins given the series outcome.

@@

\end{table}
```
With the exception of $\hat{P}^{+|k,r}_{MS}$ when $r = 10$ and when the eventual series loser is the team that wins after a streak of three round wins, all un-adjusted binomial test $p$-values are greater than the $\alpha = 0.05$ confidence level, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win proportions are different than the observed proportion. tODO: Move to Methodology. However, after adjusting the $p$-values with the Benjamini and Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.

When performing the same tests for streaks of two, four, and five, there is no case in which we can reject the binomial null hypothesis for the expected notional proportion $\hat{P}^{+|k,r}_0$ (even before the BY p-value correction). The null hypothesis can only be rejected in one extreme case for the MS proportion $\hat{P}^{+|k,r}_{MS}$.  the expected  when $k = 5, r = 7$ after applying the BY p-value correction.[^18]

### 2022-08-29 paper/paper.tex
atl fixes

We adopt the terminology ``series'' to refer to a single best-of-11
matchup, so as to mirror the terminology of playoff series in
professional leagues like the National Basketball Association (NBA),
National Hockey League (NHL), and Major League Baseball (MLB). A
``game'' or a ``match'' in such leagues is analogous to a ``round'' of
CoD SnD for the purposes of this paper.

We note that SnD is not the only game mode played in competitive
CoD.\footnote{Hardpoint has been played as the first and fourth game
  modes in a matchup. The third game mode was Domination in the 2020
  season, and Control in the 2021 and 2022 seasons.} Teams play in a
head-to-head, best-of-five format, where SnD is always played as the
second and fifth game modes. The best-of-five matchup could also be
called a ``series'', but since we analyze only the SnD games, we refer
to the SnD games as series.

@@

  Outside of tournaments, teams all play each other twice throughout the
  season, constituting qualifiers. Each team gets to play the
  higher-seeded role once in their head-to-head matchups with a given
  team, despite their win-loss records.}

@@

As implied by MS's Theorem 1, we should expect the proportion of round
wins immediately following a streak of \(k\) rounds wins for a series
lasting \(r\) rounds, \(\hat{P}^{+|k,r}_{MS}\), to be strictly less than
\(p^{+|r}\). Although one might be tempted to mirror the equal
proportions hypothesis testing performed by MS, our context is
fundamentally different from that of MS, who focus on longitudinal data
in controlled settings, unaffected by opposition.\footnote{GVT also
  perform statistical tests on shots from players in live games,
  i.e.~``observational'' data, but they note that their findings are
  likely affected by player shot selection in the face of defensive
  strategy by the opposing team.} The number of trials is fixed in their
experimental designs, but in CoD SnD, the number of rounds played is
determined as a function of the max number of possible rounds (\(s\))
and whether or not the team wins the series. The Bernoulli trial success
probability, i.e.~single round win percentage in CoD SnD, is not
independent of the opponent. Consequently, a statistical test of the
difference in \(\hat{P}^{+|k,r}\) and \(\hat{P}^{-|kr}\), as performed
by MS to evaluate their hypothesis regarding post-streak success rate,
is not completely appropriate, although useful as a reference.

@@

One can consider another form of the expected proportion of rounds won
immediately after a streak of \(k\) round wins in a best-of-\(s\) series
given the length of the series (\(r\) rounds), the ``notional''
proportion \(\hat{P}^{+|k,r}_0\). The Bernoulli round win probability
underlying \(\hat{P}^{+|k,r}_0\) is

\begin{equation}\label{eq:pwkr}
p_0(\text{win} | k, r) = p^{+|k,r}_0 := \begin{cases}
  \frac{m - k}{r - k} & \text{team wins series}, \\
  \frac{s - m - k}{r - k} & \text{team loses series},
\end{cases}
\end{equation}

We can perform a two-tailed binomial test to evaluate the null
hypothesis \(\omega = \omega_0\) for the observed probability of success
\(\omega\) and a user-specified \(\omega_0\) (where
\(0 \leq \omega_0 \leq 1\)). If there are \(r^+\) observed successes in
a sample of \(r\) trials and we expect that there should be
\(r * \omega_0\), the probability of arriving at this expected number of
successes is

@@

@@

We can further decompose Equation \ref{eq:pwkr} by the round \(i\)
(where \(i \leq r\)) in which the streak of length \(k\) carries into.

\begin{equation}\label{eq:pwkri}
p_0(\text{win} | k, r, i) = p^{+|k,r,i}_0 = \begin{cases}
  \frac{m - k}{r - k}, & \text{team wins series}, i \neq r, \\
  1, & \text{team wins series}, i = r, \\
  \frac{s - m - k}{r - k}, & \text{team loses series}, i \neq r, \\
  0, & \text{team loses series}, i = r.
\end{cases}
\end{equation}

Again, we can apply a binomial test to evaluate the hypothesis that the
expected proportions, \(\hat{P}^{+|k,r,i}_0\) and
\(\hat{P}^{+|k,r,i}_{MS}\) separately, are equal to the observed
proportion \(P^{+|k,r}\).

@@

Stepping back from the (one-sided) perspective of a single team's round
win probability when streaking, one can attempt to detect the hot hand
phenomenon more broadly with a Wald-Wolfowitz runs test. Under the null
hypothesis, the number of runs in a sequence of \(r\) trials is a random
variable that can take on values \(+\) or \(-\) and arrive at \(r^+\)
successes (\(r^- = r - r^+\) failures), with the following mean \(\mu\)
and variance \(\sigma^2\):

>>>>

We adopt the terminology ``series'' to refer to a single best-of-11
matchup, so as to mirror the terminology of playoff series in
professional leagues like the National Basketball Association (NBA),
National Hockey League (NHL), and Major League Baseball (MLB). A
``game'' or a ``match'' in such leagues is analogous to a ``round'' of
CoD SnD for the purposes of this paper. Note that SnD is not the only
game mode played in competitive CoD.\footnote{Hardpoint has been played
  as the first and fourth game modes in a matchup. The third game mode
  was Domination in the 2020 season, and Control in the 2021 and 2022
  seasons.} Teams play in a head-to-head, best-of-five format, where SnD
is always played as the second and fifth game modes. The best-of-five
matchup could also be called a ``series'', but since we analyze only the
SnD games, we refer to the SnD games as series.

@@

  Outside of tournaments, teams play each other twice throughout the
  season, constituting qualifiers. Each team gets to play the
  higher-seeded role once in their head-to-head matchups with a given
  team.

  This format has minimized the range of rates at which teams start
  series playing offense. The highest rate at which a team has started
  their series playing defense across all tournament and qualifier SnD
  series in a single season is 66\% (31 of 47). The lowest is 38\% (16
  of 42).}

@@

As implied by MS's Theorem 1, we should expect the proportion of round
wins immediately following a streak of \(k\) rounds wins for a series
lasting \(r\) rounds, \(\hat{P}^{+|k,r}_{MS}\), to be strictly less than
\(p^{+|r}\). However, we should not mirror the equal proportions
hypothesis testing performed by MS.

Our context is fundamentally different from that of MS, who focus on
longitudinal data in controlled settings, unaffected by
opposition.\footnote{GVT also perform statistical tests on shots from
  players in live games, i.e.~``observational'' data, but they note that
  their findings are likely affected by player shot selection in the
  face of tactics by the opposing team.} The number of trials is fixed
in their experimental designs, but in CoD SnD, the number of rounds
played is determined as a function of the max number of possible rounds
(\(s\)) and whether or not the team wins the series. The Bernoulli trial
success probability, i.e.~single round win percentage in CoD SnD, is not
independent of the opponent. Consequently, a statistical test of the
difference in \(\hat{P}^{+|k,r}\) and \(\hat{P}^{-|kr}\), as performed
by MS to evaluate their hypothesis regarding post-streak success rate,
is not completely appropriate, although useful as a reference.

@@

One can consider another form of the expected proportion of rounds won
immediately after a streak of \(k\) round wins in a best-of-\(s\) series
given the final length of the series (\(r\) rounds), the ``notional''
proportion \(\hat{P}^{+|k,r}_0\). The Bernoulli round win probability
underlying \(\hat{P}^{+|k,r}_0\) is

\begin{equation}\label{eq:pwkr}
p_0(\text{win} | k, r) = p^{+|k,r}_0 := \begin{cases}
  \frac{m - k}{r - k} & \text{team wins series}, r > m; \\
  1 & \text{team wins series}, r = m; \\
  \frac{s - m - k}{r - k} & \text{team loses series}, r > m + k; \\
  0 & \text{team loses series}, r = m + k,
\end{cases}
\end{equation}

where \(r \in R\) for \(m\) from Equation \ref{eq:m}.

We can perform a two-tailed binomial test to evaluate the null
hypothesis \(\omega = \omega_0\) for the observed probability of success
\(\omega\) and a user-specified \(\omega_0\) (where
\(0 \leq \omega_0 \leq 1\)). If there are \(r^+\) observed successes in
a sample of \(r\) trials, the probability of arriving at this expected
number of successes is

@@

We should expect that there should be \(r * \omega_0\) successes.

@@

We can further decompose Equation \ref{eq:pwkr} by the round \(i\)
(where \(k < i \leq r\)) in which the streak of length \(k\) carries
into.

\begin{equation}\label{eq:pwkri}
p_0(\text{win} | k, r, i) = p^{+|k,r,i}_0 = \begin{cases}
  \frac{m - k}{r - k} & \text{team wins series}, i \neq r; \\
  1 & \text{team wins series}, i = r; \\
  \frac{s - m - k}{r - k} & \text{team loses series}, i \neq r, r > m + k; \\
  0 & \text{team loses series}, i = r \text{ or } r = m + k.
\end{cases}
\end{equation}

Again, we can apply a binomial test to evaluate the hypothesis that the
expected proportion--\(\hat{P}^{+|k,r,i}_0\) and
\(\hat{P}^{+|k,r,i}_{MS}\) separately--is equal to the observed
proportion \(P^{+|k,r,i}\).

@@

Stepping back from the perspective of a single team's round win
probability when streaking, one can attempt to detect the hot hand
phenomenon more broadly with a Wald-Wolfowitz runs test. Under the null
hypothesis, the number of runs in a sequence of \(r\) trials is a random
variable that can take on values \(+\) or \(-\) and arrive at \(r^+\)
successes (\(r^- = r - r^+\) failures), with the following mean \(\mu\)
and variance \(\sigma^2\):
